---
title: "portfolio-6-thesis-graphs"
author: "Elayna Seago"
date: "4/12/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

In this portfolio I am reading in different data sets and making different kinds of graphs that I used in my thesis. The main thing that makes these graphs different from ones we have done for class is that I had a much more specific vision of how they needed to be, so I made a lot more small detail changes than I have before.

```{r libraries , echo=FALSE}

library(readxl)
library(tidyverse)

```


Graph 1
```{r read-files}

RegCoGraph <- read_excel("RegCo.xlsx")
```

```{r define-variables}
RegCoGraph$PID<-as.factor(RegCoGraph$PID)

RegCoGraph$Age <- factor(RegCoGraph$Age,
                               levels = c(1,2),
                               labels = c("Old", "Young")) 

#converts 1's and 2's in the data file to correspond to factor labels of the block type variable of study method.

RegCoGraph$Shift_type <-factor(RegCoGraph$Shift_type,
                                  levels = c(1,2),
                                  labels = c("Hold Cue", "Shift Cue")) 

#converts 1's and 2's in the data file to correspond to factor labels of the cue type variable of time.

RegCoGraph$beta_coeff <- as.numeric(RegCoGraph$beta_coeff)

#RegCo$Block_num <- factor(RegCo$Block_num,
                         # levels = 1,
                          #labels = "first hold")

RegCoGraph$SBlock_num <-factor(RegCoGraph$Block_num,
                                  levels = c(1,2,3,4),
                                  labels = c("First Mostly Hold Block", "First Mostly Shift Block" , "Second Mostly Hold Block" , "Second Mostly Shift Block"))
```


#finally started to use echo false
```{r graph-1, echo=FALSE}
facet.labs <- as_labeller(c('1' = "First Mostly Hold Block" , '2' = "First Mostly Shift Block" , '3' = "Second Mostly Hold Block" , '4' = "Second Mostly Shift Block"))

ggplot(RegCoGraph, mapping = aes(x = Shift_type , y = beta_coeff , fill = Shift_type)) +
  geom_dotplot(binaxis = "y" , stackdir = "center")+
  facet_wrap(~ Block_num , labeller = facet.labs)+
  labs(title = "Regression Coefficients for Younger and Older \nAdults During an Attention Shifting Paradigm" , x = "Cue Type" , y = "Regression Coefficient" , fill = "Cue Type")
```


Graph 2
#used means and standard error to make a dataset just for graphing because this was the easiest was for me to add error bars
```{r graph-2 , echo=FALSE}
graphable <- data.frame(
  cue = c("Hold Cue" , "Shift Cue" , "Hold Cue" , "Shift Cue") ,
  block = c("MH","MH","MS","MS"),
  response = c(87,80,76,78),
  se = c(3,4,5,6)
)

facet.labs <- as_labeller(c('MH' = "Mostly Hold Block" , 'MS' = "Mostly Shift Block"))

ggplot(graphable, mapping = aes(x = cue, y = response , fill = cue)) +
  geom_bar(stat = "summary")+
  facet_grid(.~block , labeller = facet.labs)+
  labs(title = "Older Adults Accuracy on an \nAttention Shifting Paradigm" , x = "Cue Type" , y = "Accuracy (%)")+
  scale_x_discrete(labels = c("Hold_Cue" = "Hold Cue" , "Shift_Cue" = "Shift Cue"))+
  geom_errorbar(aes(x = cue , ymin = response-se , ymax = response + se), colour = "black", width = .4)+
  scale_fill_manual(values = c("#999999" , "#E7B800" , "#999999" , "#E7B800"))+
  theme(plot.title = element_text(size = 16))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text = element_text(size = 13))+
  ylim(0,100)
```



```{r}
Young <- read_excel("young_mean_data.xlsx")
```


```{r}
Young$Block_type <- factor(Young$Block_type,
                               levels = c(1,2),
                               labels = c("Mostly_Hold_Block", "Mostly_Shift_Block")) 

#converts 1's and 2's in the data file to correspond to factor labels of the block type variable of study method.

Young$Shift_type <-factor(Young$Shift_type,
                                  levels = c(1,2),
                                  labels = c("Hold_Cue", "Shift_Cue")) 

#converts 1's and 2's in the data file to correspond to factor labels of the cue type variable of time.
```

```{r}
Young %>% 
  group_by(Block_type , Shift_type) %>% 
  summarise(mean = mean(RT) ,
            sd = sd(RT),
            se = sd / sqrt(20))
```


Graph 3- I set the axis limits so that axes would match with a graph I made for older adults
```{r}
graphable2 <- data.frame(
  Cue = c("Hold Cue" , "Shift Cue" , "Hold Cue" , "Shift Cue") ,
  block = c("MH","MH","MS","MS"),
  response = c(980,1100,1080,1040),
  se = c(40,40,60,50)
)

#myColors <- c("#999999" , "#E7B800")
#names(myColors) <-levels(graphable$cue)
#custom_colors <- scale_colour_manual(name = "Cue Type" , values = "myColors")

facet.labs <- as_labeller(c('MH' = "Mostly Hold Block" , 'MS' = "Mostly Shift Block"))

ggplot(graphable2, mapping = aes(x = Cue, y = response , fill = Cue)) +
  geom_bar(stat = "summary")+
  facet_grid(.~block , labeller = facet.labs)+
  labs(title = "Response Times for Younger Adults on an \nAttention Shifting Paradigm" , x = "Cue Type" , y = "Response Time (ms)")+
  scale_x_discrete(labels = c("Hold_Cue" = "Hold Cue" , "Shift_Cue" = "Shift Cue"))+
  geom_errorbar(aes(x = Cue , ymin = response-se , ymax = response + se), colour = "black", width = .4)+
  scale_fill_manual(values = c("#999999" , "#E7B800" , "#999999" , "#E7B800"))+
   theme(plot.title = element_text(size = 16))+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(text = element_text(size = 13))+
  ylim(0,1500)
```


```{r}
Old <- read_excel("AllOldDSC.xlsx")
```

Here, I had the rt in seconds but wanted to graph it in milliseconds. I learned you can just convert it in the graph instructions which is cool.
```{r}
Old %>% 
ggplot(aes(x = RT*1000 , y = DSC))+
  geom_point()+
  facet_wrap(~Block_type + Shift_type)+
  stat_smooth(method = "lm")+
  labs(x = "Response Time (ms)" , y = "Digist Symbol Substitution Score")

```

